Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
fixing benchmarks
added phi input to the CEGIS with AA section
replaced "isation" by "ization"

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesise safe 
digital state-feedback controls
and prove their soundness by encompassing errors due to digitalisation and quantisation effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

%To this end, we formalise the notion of solution generalisation for
%Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
%of abstraction refinement in order to achieve scalability.
%This strategy enables the inductive generalisation engine inside CEGIS
%to look for candidate solutions in a reduced solution space.

@@

%% We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
%% We then give the details of both methods of solution generalization \todo{define ``solution generalisation''} that we compare.  
%% The first checks safety by unwinding the transition relation to a completeness threshold, 
%% whereas the second employs abstract acceleration.

@@

At this point, we recap the the synthesis problem that we solve in this work:
we seek a digital feedback controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop plant model safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range, 
the reference signal to be set to zero, 
saturations on the inputs, 
and account for digitalisation and quantisation errors introduced by the controller.

@@

%% \todo{All good - only the word ``generalisation'' won't be understood by a control person (we might have reviewers from this area?). Anticipate the explanation  given below to the introduction section.}

@@

  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
  %uses a multi-staged verification phase and performs solution generalisation based on
%the plant precision, the number of loop unrollings, 
  %and the sampling rate. Essentially, it
  synthesises a controller for an individual initial state
and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
inputs, and time horizons during the verification phase.
Essentially, this approach relies on the explicit
simulation over a bounded time horizon of individual states that form
part of an uncountable space and tries to generalize it for an
infinite space over an infinite time horizon.

>>>>

We describe and evaluate two approaches for synthesizing digital controllers for state-space physical plants, 
both based on the Counter-Example Guided Inductive Synthesis (CEGIS)~\cite{sketch} architecture, recently of wide use for program synthesis.   
We provide two alternative automated procedures to synthesise safe 
digital state-feedback controls
and prove their soundness by encompassing errors due to digitalization and quantization effects that are present in the digital controller interacting with the continuous plant. 
% computations and representations of dynamics, providing sufficient conditions for sound and complete safe solutions for the state feedback control problem.

@@

%To this end, we formalise the notion of solution generalization for
%Counter-Example Guided Inductive Synthesis (CEGIS), which makes use 
%of abstraction refinement in order to achieve scalability.
%This strategy enables the inductive generalization engine inside CEGIS
%to look for candidate solutions in a reduced solution space.

@@

%% We outline the general architecture of the program synthesizer used in both approaches \todo{which approaches - pls recall or clarify}. 
%% We then give the details of both methods of solution generalization \todo{define ``solution generalization''} that we compare.  
%% The first checks safety by unwinding the transition relation to a completeness threshold, 
%% whereas the second employs abstract acceleration.

@@

At this point, we recap the the synthesis problem that we solve in this work:
we seek a digital feedback controller $K$ (see Eq.~\ref{eq:controlaction})
that makes the closed-loop plant model safe for 
initial state $x_0$, reference signal $r_k$ and input $u_k$
as defined in Sec.~\ref{ssec:safety}. 
We consider non-deterministic initial states within a specified range, 
the reference signal to be set to zero, 
saturations on the inputs, 
and account for digitalization and quantization errors introduced by the controller.

@@

%% \todo{All good - only the word ``generalization'' won't be understood by a control person (we might have reviewers from this area?). Anticipate the explanation  given below to the introduction section.}

@@

  The naive approach described in Sec.~\ref{sec:CEGIS-precision-incrementation}
  %uses a multi-staged verification phase and performs solution generalization based on
%the plant precision, the number of loop unrollings, 
  %and the sampling rate. Essentially, it
  synthesises a controller for an individual initial state
and input with a bounded time horizon and, subsequently, it generalizes it to all reachable states,
inputs, and time horizons during the verification phase.
Essentially, this approach relies on the explicit
simulation over a bounded time horizon of individual states that form
part of an uncountable space and tries to generalize it for an
infinite space over an infinite time horizon.
